Temperature Measurements in Optical Tweezer Experiments

### 2017-01-19 doc/draft1.tex
new plots, new updates

\textit{interacing}

>>>>

\textit{interacing}. One such histogram can be seen in fig.~\ref{fig:histogram}.
        \includegraphics[scale=0.4]{images/histogram.pdf}
        \caption{Histogram of total energies for incoming (red) and outgoing (blue) particles. The parameters for this histogram are $\Delta Q^*=0.04$,
        $T_\text{ambient}^*=0.08$, $P^*=0.8$. What can be seen here is that the outgoing particles have a higher count of particles with more total
    energy.}
        \label{fig:histogram}
